Dirac integration with a general purpose bookkeeping DB: a complete general suite for distributed resources exploitation

### 2013-10-24 CHEP2013/paper/long-paper.tex
final CHEP2013

\author{M Chrzaszcz$^{1,2}$, C De Santis$^3$, G Donvito$^4$, A Fella$^{5,6}$, R Grzymkowski$^2$, B Santeramo$^{4,7}$, L Tomassetti$^{6,8}$, M Zdybal$^2$}
\address{$^1$ Physik-Institut, Universitat Zurich, Zurich, Switzerland}
\address{$^2$ Henryk Niewodniczanski Institute of Nuclear Physics Polish Academy of Sciences, Krakow, Poland}
\address{$^3$ INFN - Sezione di Roma Tor Vergata, Roma, Italy}
\address{$^4$ INFN - Sezione di Bari, Bari, Italy}
\address{$^5$ INFN - Sezione di Pisa, Pisa, Italy}
\address{$^6$ Dipartimento di Matematica e Informatica, Universit\'a di Ferrara, Ferrara, Italy}
\address{$^7$ Dipartimento Interateneo di Fisica dell’Universit\'a e del Politecnico di Bari, Bari, Italy}
\address{$^8$ INFN - Sezione di Ferrara, Ferrara, Italy}
\ead{bruno.santeramo@ba.infn.it}

>>>>

\author{F Bianchi$^{a,b}$, M Chrzaszcz$^{c,d}$, V Ciaschini$^e$, M Corvo$^f$, C De Santis$^{g,h}$, D Del Prete$^i$, A Di Simone$^{g,h}$, G Donvito$^l$, A Fella$^{m,n}$, P Franchini$^e$, F Giacomini$^e$, A Gianelle$^f$, R Grzymkowski$^d$, S Longo$^f$, S Luitz$^o$, E Luppi$^{p,q}$, M Manzali$^{p,q}$, M Rama$^f$, G Russo$^i$, S Pardi$^i$, L Perez Perez$^m$, B Santeramo$^{l,s}$, R Stroili$^f$, L Tomassetti$^{n,q}$, M Zdybal$^d$}
\address{$^a$ University of Torino, Turin, Italy}
\address{$^b$ INFN - Sezione di Torino, Turin, Italy}
\address{$^c$ Physik-Institut, Universitat Zurich, Zurich, Switzerland}
\address{$^d$ Henryk Niewodniczanski Institute of Nuclear Physics Polish Academy of Sciences, Krakow, Poland}
\address{$^e$ INFN - CNAF, Bologna, Italy}
\address{$^f$ INFN - Sezione di Padova, Padua, Italy}
\address{$^g$ INFN - Sezione di Roma Tor Vergata, Roma, Italy}
\address{$^h$ Department of Physics, University of Rome Tor Vergata, Rome, Italy}
\address{$^i$ INFN – Sezione di Napoli, Naples, Italy}
\address{$^l$ INFN - Sezione di Bari, Bari, Italy}
\address{$^m$ INFN - Sezione di Pisa, Pisa, Italy}
\address{$^n$ Department of Mathematics and Computer Science, University of Ferrara, Ferrara, Italy}
\address{$^o$ SLAC, USA}
\address{$^p$ Department of Physics, University of Ferrara, Ferrara, Italy}
\address{$^q$ INFN - Sezione di Ferrara, Ferrara, Italy}
\address{$^r$ INFN LNF – Frascati, Italy}
\address{$^s$ Department of Physics, University and Polytechnic of Bari, Bari, Italy}
\ead{bruno.santeramo@ba.infn.it}
